% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textheight}{10in} % increase text height to fit on 1-page 
\addtolength{\topmargin}{-.5in}
\addtolength{\topsep}{-1mm}

\usepackage{hyperref}
\usepackage{enumitem}

\begin{document} 

\name{HARRISON J. GOLDSTEIN}
              
\begin{resume}

\begin{ncolumn}{3}
  \textbf{PRESENT ADDRESS} & hgoldstein95@gmail.com & \textbf{PERMANENT ADDRESS} \\
  3639 Clara Dickson Hall & (732).977.7316 & 15 Monarch Ln. \\
  Ithaca, NY 14853 & www.harrisongoldstein.me & Freehold, NJ 07728 \\
\end{ncolumn}

\section{EDUCATION}
	{\bf CORNELL UNIVERSITY}, College of Engineering, Ithaca, NY \\
	Pursuing Bachelor of Science in Computer Science: Class of 2018 \\
	G.P.A. 3.9/4.0 \vspace{5pt}\\
	{\bf MANALAPAN HIGH SCHOOL}, Science and Engineering Learning Center, Englishtown, NJ \\
	Diploma: June 2014

\section{RELEVANT COURSEWORK}
  Honors Object Oriented Programming and Data Structures, Digital Logic and Computer Organization, Foundations of Engineering Leadership, Discrete Structures, UNIX Tools and Scripting
 
\section{WORK EXPERIENCE}
  \vspace{-5pt}	
  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.4in}\= \kill % set up two tab positions
    {\bf Developer} \>{\bf TIMAN LLC, Freehold, NJ} \>Summer 2014-Present\\
  \end{tabbing}\vspace{-15pt}
  \begin{itemize}[leftmargin=*, nolistsep]
    \item[-] Designed systems to automate financial data acquisition and manipulation, for more efficient company stock valuation.
    \item[-] Created a Python web scraper and resolved compatibility issues between Windows and OSX. The Python portion was completed over the course of two months.
    \item[-] Created a Java version of the scraper which included a JavaFX GUI and more efficient scraping.
  \end{itemize}
   
    
\section{PROJECTS}    
	\vspace{-5pt}
	\begin{tabbing}
    \hspace{2.3in}\= \hspace{2.4in}\= \kill
    {\bf Designer} \>{\bf ASL Interpreting Glove} \>Fall 2013\\
  \end{tabbing}\vspace{-15pt}
  \begin{itemize}[leftmargin=*, nolistsep]
    \item[-] Partnered with a fellow student to design and build a glove that interpreted American Sign Language letters.
    \item[-] Designed and built sensor circuits for measuring features of hand positions, including finger bend and finger proximity.
    \item[-] Developed code in C that read data from a TI-MSP430 microcontroller, and code in Python that interpreted those signals based on mathematical models.
    \item[-] Project was completed in the Science and Engineering Learning Center at Manalapan High School.
  \end{itemize}
  \vspace{-10pt}
  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.4in}\= \kill
    {\bf Programmer} \>{\bf an$\backslash$note} \>Fall 2014\\
  \end{tabbing}\vspace{-15pt}
  \begin{itemize}[leftmargin=*, nolistsep]
    \item[-] Collaborated with a team to create an$\backslash$note, a note-taking web application created for High School and University students.
    \item[-] Designed a Javascript interpreter that converted plaintext input into formatted and organized output. Also worked on HTML and CSS elements of the site.
    \item[-] Project was completed at Big Red Hacks 2014 over the course of 48 hours.
  \end{itemize}
  \vspace{-10pt}
  \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.4in}\= \kill
    {\bf Programmer} \>{\bf n-Body Simulation} \>Spring 2014\\
  \end{tabbing}\vspace{-15pt}
  \begin{itemize}[leftmargin=*, nolistsep]
    \item[-] Partnered with a fellow student to create a Python simulation of the \"n-body problem\", a common problem in physics that can be modeled as n planets in gravitational orbit.
    \item[-] Used the classical Runge-Kutta method to calculate planet positions over time, and vPython to generate a 3D graphical representation.
    \item[-] Project was completed in the Science and Engineering Learning Center at Manalapan High School.
  \end{itemize}
 
\section{HONORS AND AWARDS}
	Eagle Scout, Boy Scouts of America \\
	AP Scholar with Distinction, College Board \\
	State 1st Prize Engineering Design, Technology Students Assn.

\section{SKILLS AND COMPETENCIES}
  Java 7 and 8, Python 2.7 and 3.4, C++, HTML5, CSS3/SASS, \LaTeX \\
  Circuit Prototyping, 3D Printing Design, Object Oriented Programming \\
  Soldering, Carpentry, Machining \\
  Public Speaking
	
\end{resume}
\end{document}
