\documentclass[a4paper]{article}

\usepackage{FiraSans}
\usepackage[
  defaultfam,
  tabular,
  lining
]{montserrat}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\fontfamily{Montserrat-TOsF}\selectfont #1}}
\usepackage[top=0.5in,bottom=1in,left=0.5in,right=0.5in]{geometry}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{setspace}
\usepackage{fancyhdr}

\newcommand{\semibf}{\fontseries{semibold}\selectfont}

\renewcommand{\arraystretch}{2}

\titleformat{\section}{\normalfont\Large\bfseries\fontfamily{FiraSans-TLF}\selectfont}{\thesection.}{1em}{}
\titleformat{\subsection}{\normalfont\large\bfseries\fontfamily{FiraSans-TLF}\selectfont}{\thesection.}{1em}{}

\begin{document}

\noindent
{\fontfamily{FiraSans-TLF}\selectfont
\begin{minipage}[t]{.5\textwidth}
  \vspace{0pt}
  {\Huge {\textbf{Harrison}} Goldstein} \\
  {\Large Assistant Professor, University at Buffalo}
\end{minipage}
\begin{minipage}[t]{.5\textwidth}
  \vspace{0pt}
  \flushright
  {\large \href{https://harrisongoldste.in}{https://harrisongoldste.in}} \\
  {\large \href{mailto:hgoldste@buffalo.edu}{hgoldste@buffalo.edu}} \\
\end{minipage}}


\section*{Current Position}
\noindent {\bf University at Buffalo, SUNY} \\
Department of Computer Science and Engineering \\
Assistant Professor

\section*{Education and Past Academic Positions}
\noindent {\bf University of Maryland, College Park} \\
Victor Basili Postdoctoral Research Fellow \\
Advised by Leonidas Lampropoulos

\bigskip
\noindent {\bf University of Pennsylvania} \\
Ph.D. in Computer Science \\
Advised by Benjamin C. Pierce

\bigskip
\noindent {\bf Cornell University} \\
M.Eng., B.S. in Computer Science \\
Advised by Adrian Sampson


\noindent 

\section*{Publications, Talks, and Grants}
\subsection*{Dissertation}
\href{https://repository.upenn.edu/entities/publication/72ca3499-c5f6-4fc1-b5a3-9d66d8dd534e}{\bf Property-Based Testing for the People} \\
{\semibf Harrison Goldstein} {\em advised by} Benjamin C. Pierce \\
University of Pennsylvania, Defended May 24, 2024

\subsection*{Referreed Conference and Journal Publications}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  JFP & {\bf Etna: An Evaluation Platform for Property-Based Testing} \newline
    A. Keles, J. Shi, N. Kamath, T. N. Liu, C. Mert, {\semibf H. Goldstein}, B. C. Pierce, L. Lampropoulos \newline
    Journal of Functional Programming. May 2026. 22 pages.
    \\
  PLDI'26 &
  \href{https://doi.org/10.1145/3808329}{\bf The Search for Constrained Random Generators} \newline
    {\semibf H. Goldstein}, H. Peleg, C. Torczon, D. Sainati, L. Lampropoulos, B. C. Pierce \newline
    Programming Language Design and Implementation (PLDI) 2026. 25 pages.
    \\
  OOPSLA'26 &
  \href{https://dl.acm.org/doi/pdf/10.1145/3798263}{\bf Fail Faster: Staging and Fast Randomness for High-Performance PBT} \newline
    Cynthia Richey, Joseph W. Cutler, {\semibf Harrison Goldstein}, Benjamin C. Pierce \newline
    Obj.-Oriented Programming, Systs., Langs., and Apps. (OOPSLA) 2026. 25 pages.
    \\
  ICFP'26 \newline {\scriptsize \semibf{Conditional}}&
  \href{https://arxiv.org/abs/2602.18545}{\bf Programmable Property-Based Testing} \newline
    Alperen Keles, Justine Frank, Ceren Mert, {\semibf Harrison Goldstein}, Leonidas Lampropoulos \newline
    International Conference on Functional Programming (ICFP) 2026. 25 pages.
    \\
  OOPSLA'25 &
  \href{https://dl.acm.org/doi/abs/10.1145/3763082}{\bf Tuning Random
  Generators: Property-Based Testing as Probabilistic Programming} \newline
    R. Tjoa, P. Garg, {\semibf H. Goldstein}, T. Millstein, B. C. Pierce, G. Van den Broek \newline
    Obj.-Oriented Programming, Systs., Langs., and Apps. (OOPSLA) 2025. 25 pages.
    \\
  OOPSLA'25 &
    \href{https://dl.acm.org/doi/10.1145/3720426}{\bf QED in Context: An Observation Study of Proof Assistant Users} \newline
    Jessica Shi, Cassia Torczon, {\semibf Harrison Goldstein}, Benjamin C. Pierce, Andrew
    Head \newline
    Obj.-Oriented Programming, Systs., Langs., and Apps. (OOPSLA) 2025. 25 pages.
    \\
  UIST'25 &
    \href{https://dl.acm.org/doi/10.1145/3746059.3747739}{\bf FEDT: Supporting
    experiment design and execution in HCI fabrication research} \newline
    V. Savage, {\semibf H. Goldstein}, N. P\"us\"ok, J. Ren, B. Dutt, C. Nandi,
    L. Oehlberg \newline
    User Interface Software and Technology (UIST) 2025. 13 pages. \\
  CCS'25 &
  \href{https://dl.acm.org/doi/10.1145/3719027.3765055}{\bf A Qualitative Analysis of Fuzzer Usability and Challenges} \newline
    Y. Zhao, W. Guo, {\semibf H. Goldstein}, D. Votipka, K. R. Fulton, M. Mazurek \newline
    Conference on Computer and Communications Security (CCS) 2025. 13 pages.
    \\
  UIST'24 &
    \href{https://dl.acm.org/doi/10.1145/3654777.3676407}{\bf Tyche: Making
    Sense of Property-Based Testing Effectiveness} \newline
    {\semibf Harrison Goldstein}, Jeffrey Tao, Zac Hatfield-Dodds, Benjamin C.
    Pierce, Andrew Head \newline
    User Interface Software and Technology (UIST) 2024. 13 pages.
    \\
  PLDI'24 &
    \href{https://dl.acm.org/doi/10.1145/3656434}{\bf Stream
    Types} \newline
    J. W. Cutler, C. Watson, E. Nkurumeh, P. Hilliard, {\semibf H. Goldstein}, C.
    Stanford, B. C. Pierce \newline
    Programming Language Design and Impl. (PLDI) 2024. 24 pages.
    \\
  PLDI'24 &
    \href{https://dl.acm.org/doi/10.1145/3656410}{\bf Daedalus: Safer Document Parsing} \newline
    I. Diatchki, M. Dodds, {\semibf H. Goldstein}, B. Harris, D. Holland, B. Razet, C.
    Schlesinger, S. Winwood \newline
    Programming Language Design and Implementation (PLDI) 2024. 24 pages.
    \\
  ICSE'24 \newline {\scriptsize \semibf{Distinguished}} &
    \href{https://dl.acm.org/doi/10.1145/3597503.3639581}{\bf Property-Based
    Testing in Practice} \newline
    {\semibf Harrison Goldstein}, Joseph W. Cutler, Daniel Dickstein, Benjamin C. Pierce,
    Andrew Head \newline
    International Conference on Software Engineering (ICSE) 2024. 23 pages.
    \\
  ICFP'23 \newline {\scriptsize \semibf{Distinguished}} &
    \href{https://dl.acm.org/doi/10.1145/3607842}{\bf Reflecting on Random Generation} \newline
    {\semibf Harrison Goldstein}, Samantha Frohlich, Meng Wang, Benjamin C.
    Pierce \newline
    International Conference on Functional Programming (ICFP) 2023. 34 pages.
    \\
  OOPSLA'22 &
    \href{https://dl.acm.org/doi/10.1145/3563291}{\bf Parsing Randomness} \newline
    {\semibf Harrison Goldstein}, Benjamin C. Pierce \newline
    Obj.-Oriented Programming, Systs., Langs., and Apps. (OOPSLA) 2022. 25 pages.
    \\
  ESOP'21 &
    \href{https://link.springer.com/chapter/10.1007/978-3-030-72019-3_10}{\bf Do Judge a Test
    by its Cover: Combining Combinatorial and Property-Based Testing} \newline
    {\semibf Harrison Goldstein}, John Hughes, Leonidas Lampropoulos, Benjamin
    C. Pierce \newline
    European Symposium on Programming (ESOP) 2021. 27 pages.
\end{longtable}

\subsection*{Workshop Papers and Experience Reports}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  PLATEAU'26 &
    {\bf Aporia: Asking Questions to Elicit User Decisions} \newline
    Saketh Kasibatla, Sorin Lerner, Hila Peleg, Benjamin Pierce, {\semibf Harrison Goldstein} \newline
    PLATEAU Workshop 2026. 10 pages.
    \\
  PLATEAU'26 &
    \href{https://doi.org/10.1184/R1/31816747}{\bf What's in a specification?: Exploring Student Conceptions of Formal Specifications} \newline
    {\semibf Harrison Goldstein}, Cameron Moy, Daniel Patterson \newline
    PLATEAU Workshop 2026. 4 pages.
    \\
  DBTest'26 &
    \href{https://arxiv.org/abs/2604.16373}{\bf DIRT: Database-Integrated Random Testing} \newline
    Alperen Keles, Ethan Chou, {\semibf Harrison Goldstein}, Leonidas Lampropoulos
    DBTest Workshop 2026. 7 pages.
    \\
  PLATEAU'25 &
    \href{https://doi.org/10.1184/R1/29087003}{\bf Designing Proof Deautomation in Rocq} \newline
    Jessica Shi, Cassia Torczon, {\semibf Harrison Goldstein}, Benjamin C. Pierce, Andrew Head \newline
    PLATEAU Workshop 2025. 12 pages.
    \\
  OCaml'24 &
    \href{https://arxiv.org/abs/2408.14561}{\bf Mica: Automated Differential Testing for OCaml Modules} \newline
    Ernest Ng, {\semibf Harrison Goldstein}, Benjamin C. Pierce \newline
    OCaml Workshop 2024. 2 pages.
    \\
  ICFP'23 &
    \href{https://dl.acm.org/doi/abs/10.1145/3607860}{\bf Etna: An Evaluation Platform for Property-Based Testing (Experience Report)} \newline
    J. Shi, A. Kelles, {\semibf H. Goldstein}, B. C. Pierce, L. Lampropoulos \newline
    International Conference on Functional Programming (ICFP) 2023. 17 pages.
    \\
  HATRA'22 &
    \href{https://harrisongoldste.in/papers/hatra2022.pdf}{\bf Some Problems with Properties: A Study on Property-Based Testing in Industry} \newline
    {\semibf Harrison Goldstein}, Joseph W. Cutler, Adam Stein, Benjamin C. Pierce, Andrew Head \newline
    Human Aspects of Types and Reasoning Assistants (HATRA) 2022. 8 pages.
    \\
  SysML'18 &
    \href{https://mlsys.org/Conferences/doc/2018/56.pdf}{\bf Programming Language Support for Natural Language Interaction} \newline
    Alex Renda, {\semibf Harrison Goldstein}, Sarah Bird, Chris Quirk, Adrian Sampson \newline
    Conference on Machine Learning and Systems (SysML) 2018. 3 pages.
\end{longtable}

\subsection*{Demos}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  SCF'24 &
    \href{https://dl.acm.org/doi/10.1145/3665662.3673270}{\bf Supporting Characterization Experiments in Fabrication Research} \newline
    V. Savage, N. Püsök, {\semibf H. Goldstein}, C. Nandi, J. Yi Ren and L. Oehlberg \newline
    Symposium on Computational Fabrication (SCF) 2024.
    \\
  UIST'23 &
    \href{https://dl.acm.org/doi/10.1145/3586182.3615788}{\bf Tyche: In Situ Analysis of Random Testing Effectiveness} \newline
    {\semibf Harrison Goldstein}, Benjamin C. Pierce, Andrew Head \newline
    User Interface Software and Technology (UIST) 2023.
\end{longtable}

\subsection*{Talks and Podcasts}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  Talk &
    \href{https://www.youtube.com/watch?v=AFbnS9xuPhY}{\bf Metaprogramming the Next Generation of Testing Tools} \newline
    {\semibf Harrison Goldstein} \newline
    Lean Together 2026
    \\
  Talk \newline {\scriptsize Invited} &
    {\bf Property-Based Testing for the People} \newline
    {\semibf Harrison Goldstein} \newline
    Cornell + UT Software Engineering Seminar
    \\
  Talk &
    \href{https://youtu.be/c5LOYzZx-0c?si=RErfTr9vxlD_xHsY}{\bf The Best New Programming Language is a Proof Assistant} \newline
    {\semibf Harrison Goldstein} \newline
    DC Systems 006
    \\
  Podcast \newline {\scriptsize Invited} &
    \href{https://haskell.foundation/podcast/59/}{\bf Haskell Interlude \#59} \newline
    Samantha Frohlich, Wouter Swierstra, {\semibf Harrison Goldstein} \newline
    Haskell Interlude Podcast, December 2024
    \\
  Talk \newline {\scriptsize Invited} &
    \href{https://www.youtube.com/live/pS_vJAwjcM4?si=yK18h_Y9ak2ZVhMF&t=26173}{\bf My PhD Compass: 6 Ways to Guide a PhD Towards Success} \newline
    {\semibf Harrison Goldstein} \newline
    PL Mentoring Workshop @ ICFP, September 2024
    \\
  Podcast \newline {\scriptsize Invited} &
    \href{https://disseminatepodcast.podcastpage.io/episode/harry-goldstein-property-based-testing-55}{\bf Disseminate \#55} \newline
    Jack Waudby, {\semibf Harrison Goldstein} \newline
    Disseminate Podcast, June 2024
    \\
  Talk &
    {\bf Usable Property-Based Testing} \newline
    {\semibf Harrison Goldstein} \newline
    Amazon Web Services, June 2024
    \\
  Talk \newline {\scriptsize Invited} &
    \href{https://www.youtube.com/watch?v=sSl-856qUOA}{\bf Consider Collaboration} \newline
    Samantha Frohlich, {\semibf Harrison Goldstein} \newline
    PL Mentoring Workshop @ POPL, January 2024
    \\
  Talk \newline {\scriptsize Invited} &
    {\bf Advancing Property-Based Testing in Theory and Practice} \newline
    {\semibf Harrison Goldstein} \newline
    Microsoft Research, UC Berkeley, Galois, Inc., UCSC, University of Bristol
    \\
  Talk &
    {\bf Property-Based Testing in Practice} \newline
    {\semibf Harrison Goldstein} \newline
    Jane Street Programming Languages Colloquium, December 2023
    \\
  Podcast \newline {\scriptsize Invited} &
    \href{https://youtu.be/tEXq-eSiFwk?si=0tmSmEp2oK5Ucv4n}{\bf TheForkJoin \#2} \newline
    Oliver Flatt, Rachit Nigam, {\semibf Harrison Goldstein} \newline
    TheForkJoin Podcast, July 2024
    \\
  Talk &
    \href{http://njpls.org/oct22.html#goldstein}{\bf Some Problems with Properties} \newline
    {\semibf Harrison Goldstein} \newline
    NJPLS, October 2022
    \\
  Talk &
    \href{http://njpls.org/may22.html#goldstein}{\bf Reflecting on Random Generation} \newline
    {\semibf Harrison Goldstein} \newline
    NJPLS, May 2022
\end{longtable}

\subsection*{Posters}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  ICFP'21 &
    \href{https://harrisongoldste.in/papers/icfpsrc21.pdf}{\bf Ungenerators} \newline
    {\semibf Harrison Goldstein} \newline
    ICFP 2021
    \\
  POPL'20 &
    \href{https://harrisongoldste.in/papers/poplsrc20.pdf}{\bf Algebraic Combinatorial Testing} \newline
    {\semibf Harrison Goldstein} \newline
    POPL 2020
\end{longtable}

\subsection*{Misc.}
\vspace{-5mm}
\begin{longtable}{@{}p{.11\textwidth}p{.89\textwidth}@{}}
  Blog Post &
  \href{https://blog.sigplan.org/2025/09/16/think-globally-discuss-pl-locally/}{\bf
  Think Globally, Discuss PL Locally} \newline
    {\semibf Harrison Goldstein}, Michael Greenberg, Noam Zilberstein \newline
    SIGPLAN PL Perspectives Blog, September 2025
  \\
  Draft &
    \href{https://harrisongoldste.in/papers/drafts/wpe-ii.pdf}{\bf Delimited Continuations and Monads} \newline
    {\semibf Harrison Goldstein} \newline
    Unpublished PhD Milestone Draft, April 2021
  \\
  SIGBOVIK'21 &
    \href{https://harrisongoldste.in/papers/cha-cha-slide.pdf}{\bf Everybody
    Clap Your Hands: The Cha-Cha Slide is Turing Complete} \newline
    {\semibf Harrison Goldstein} \newline
    Conf. of the ACH Special Interest Group on Harry Q. Bovik (SIGBOVIK) 2021. 5 pages.
    \\
  Blog Post &
    \href{https://blog.sigplan.org/2021/03/25/conferences-after-covid-an-early-career-perspective/}{\bf Conferences after COVID: An Early Career Perspective} \newline
    J. W. Cutler, {\semibf H. Goldstein}, A. K. Hirsch, J. Hong, C. Nandi \newline
    SIGPLAN PL Perspectives Blog, March 2021
\end{longtable}

\section*{Funded Grant Proposals}
\noindent {\bf Amazon Gift: A Unified Framework for Automated Test Input
Generation Using Lean} \\
Spring 2026 \\
Secured funding from AWS to fund work on the next generation of property-based
testing automation. This work includes new proof foundations for PBT generators,
as well as new techniques for automatically obtaining generators for real
testing use-cases. \\
Team: Michael Hicks (co-PI), {\semibf Harrison Goldstein} (co-PI), Benjamin C.
Pierce (co-PI)

\bigskip
\noindent {\bf NSF \#2402449 SHF: Medium: Usable Property-Based Testing} \\
2023-2024 \\
Made significant contributions, in the form of both research project ideas and
grant writing, to help secure a NSF Medium grant. This grant helped to fund my
dissertation work, and it will continue to fund follow-on projects. \\
Team: Benjamin Pierce (co-PI), Andrew Head (co-PI), {\semibf Harrison Goldstein}
(contributor)

\newpage
\bigskip
\noindent {\bf Amazon Research Award: TYCHE: An IDE for Property-Based Testing} \\
Spring 2023 \\
Secured funding from AWS to fund my ongoing work on user interfaces for
property-based testing. This award includes the opportunity to collaborate with
contacts at AWS, including Michael Hicks, on interfaces that support real
industrial workloads. \\
Team: {\semibf Harrison Goldstein} (primary author), Benjamin Pierce (co-PI),
Andrew Head (co-PI)

\section*{Awards and Honors}

\noindent {\bf John C. Reynolds Doctoral Dissertation Award 2025} \\
ACM Special Interest Group on Programming Languages

\bigskip
\noindent {\bf Morris and Dorothy Rubinoff Award 2024} \\
University of Pennsylvania, Department of Computer and Information Science

\bigskip
\noindent {\bf Victor Basili Postdoctoral Fellowship} \\
University of Maryland, Computer Science Department

\bigskip
\noindent {\bf Certificate in Engineering Leadership} \\
Cornell Engineering Leadership Certification Program

\bigskip
\noindent {\bf 1500 Day Crossword Streak} \\
New York Times Games

\section*{Teaching and Advising}

\subsection*{Current PhD Students}

\noindent Julia Montuori-Ahuja

\bigskip

\noindent Francille Zhuang

\bigskip
\noindent Cassia Torczon (Coadvised with Benjamin C. Pierce)

\subsection*{Graduate Advisees}

\noindent Collaborator and Research Mentor, Segev Elazar Mittelman

\bigskip
\noindent Collaborator and Research Mentor, Caspar Popova

\bigskip
\noindent Collaborator and Research Mentor, Alperen Keles

\bigskip
\noindent Collaborator and Research Mentor, Pierce Darragh

\bigskip
\noindent Collaborator and Research Mentor, Ryan Tjoa

\bigskip
\noindent Collaborator and Research Mentor, Joseph W. Cutler

\bigskip
\noindent Collaborator and Research Mentor, Jessica Shi

\bigskip
\noindent Masters Co-Advisor, Ernest Ng


\subsection*{Courses}

\noindent UB CSE 305 "Introduction to Programming Languages" \\
Undergraduate Course, Spring 2026

\bigskip
\noindent UB CSE 702 "Effective and Usable Formal Methods" \\
Graduate Seminar, Fall 2025

\bigskip
\noindent Penn CIS 552 "Advanced Programming" \\
Prof. Stephanie Weirich \\
Head TA 2020-2021

\bigskip
\noindent Penn CIS 810 "Writing and Speaking with Style" \\
Prof. Benjamin C. Pierce \\
Head TA 2021

\bigskip
\noindent Cornell CS 3110 "Functional Programming" \\
Prof. Nate Foster \\
Head TA 2017

\bigskip
\noindent Cornell Engineering Leadership \\
Profs. Erica Dawson and Werner Zorman \\
Head TA 2017

\bigskip
\noindent Cornell CS 2112 “Object-Oriented Design and Data Structures (Honors)” \\
Prof. Dexter Kozen \\
TA 2016

\section*{Service}

\subsection*{Conference Organizing and Reviewing}

\noindent Steering Committee Member, Upstate PL — Ongoing

\bigskip
\noindent PC Member, OOPSLA 2026

\bigskip
\noindent PC Member, PLDI 2025

\bigskip
\noindent PC Member, PLATEAU 2025

\bigskip
\noindent Steering Committee Member, NJPLS

\bigskip
\noindent Student Reviewer, PLATEAU 2024

\bigskip
\noindent Co-Organizer, Celebration for Benjamin Pierce’s 60th Birthday

\bigskip
\noindent PC Member, HATRA 2023

\bigskip
\noindent Organizer, NJPLS 2023

\bigskip
\noindent Social Chair, POPL 2021

\bigskip
\noindent A/V Coordinator, ICFP 2021

\subsection*{Mentorship}

\noindent Ph.D. Mentor, SIGPLAN-M --- Ongoing

\bigskip
\noindent Mentor, Cornell COMPASS Program, Spring 2026

\bigskip
\noindent Speaker, PL Mentoring Workshop @ ICFP 2024

\bigskip
\noindent Ph.D. Mentor, Penn CIS Mentoring

\bigskip
\noindent Speaker, PL Mentoring Workshop @ POPL 2024

\bigskip
\noindent Research Mentor, REPL REU 2023

\bigskip
\noindent Research Mentor, DeepSpec REU

\subsection*{Misc.}

\noindent Editor in Chief, PLClub Blog 2021-2024

\section*{Employment}

\noindent {\bf University at Buffalo, SUNY} \\
Assistant Professor 2025--

\bigskip
\noindent {\bf University of Maryland, College Park} \\
Victor Basili Postdoctoral Fellow 2024-2025 \\
Working with Prof. Leonidas Lampropoulos on topics related to usable
property-based testing.

\bigskip
\noindent {\bf Galois, Inc.} \\
Research Intern 2023 \\
Worked on two research papers related to the SafeDocs DARPA program. Provided
expertise on testing that helped situate the papers in the broader research
context.

\bigskip
\noindent {\bf Amazon Web Services} \\
Research Intern 2020 \\
Worked on Zelkova, a tool for analyzing and proving properties about AWS access
policies. Encoded logical constraints from access policies as SMT formulas, in
order to infer policy implications.

\bigskip
\noindent {\bf Broadway Technology} \\
Software Engineer and Software Engineering Intern 2017--2019 \\
Built mission-critical internal tools for the company’s financial personnel, in
particular facilitating a transition to new financial tracking software.
Designed and implemented data connectors, financial calculations, web
interfaces, and more.

\bigskip
\noindent {\bf Susquehanna International Group, LLC} \\
Technology Intern 2016 \\
Helped to implement a safety system, protecting the firm from anomalous trading
behaviors. Built an engine for executing business rules as monitors for live
trading activities.

\bigskip
\noindent {\bf Last Second Beach, LLC} \\
Chief Technology Officer 2015--2016 \\
Helped to lead a small, early stage start-up, focused on providing one-price
vacations. Built a demo iOS application, helping the company to win a \$25,000
grant as part of a Business Plan Competition.


\end{document}